Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
Spelling and Grammar check

\section{Introduction}
Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics. These methods are of great interest in computer graphics for two reasons: First, they provide us with  new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.

In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment. Given an object one must find a spatially varying material distribution that satisfies some given criteria. The algorithms that solve these problems are often complicated to develop, implement, test and modify. We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new algorithms.

@@

Fabricating objects with desired deformation characteristics has been explored less in the literature. Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a desired shape while inflated ~\cite{sko:2012}. Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.

@@

Below we will describe the key components of our framework and its associated API. We begin by describing the data structures that tie our framework together, the Reducer Network and the Tuner Network. We will then show how these two components interact to provide a compact graphical description of the material assignment problem. Finally we will show our basis set of components that we use to produce a wide-range of fabrication algorithms. 

@@

$\lambda$ can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $ \boldsymbol{\theta}$. We allow our material assignment nodes to assign a void material to regions of the mesh. This allows us to treat surface displacements and material assignments in a unified fashion. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

@@

\subsection{Tuners}
We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.  Specifically a tuner is comprised of an optimization scheme, an error metric and a goal. Each tuner is attached to a specific geometric node in the Reducer Network. It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node. One can think of this as a self-tuning shader network.  This organizational structure allows us to easily optimize subdomains of our object using different tuners. We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing. 
\subsection{Tuning the Reducer Network}
\autoref{fig:tuner0} shows a typical workflow for a tuner.
\begin{figure}
\includegraphics[width=0.4\textwidth]{figure/tuner0.png}
\caption{Typical workflow for a Tuner.}
\label{fig:tuner0}
\end{figure}
A Tuner initializes its optimization procedure by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables. The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables. 
With the search space specified, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine. 
The call-back function typically performs the following three steps:
using Reducer Node to convert a variable assignment back to material assignment
function $\lambda$, running simulation with the new material assignment
and computing errors given the simulated result.
We note that our material function $\lambda$ can 
be efficiently evaluated by traversing the Reducer Network.
%I need to think about this
%We note that gradient computation of our material function $\lambda$ can also 
%be performed by efficiently traversing the Reducer Network.
\subsection{Tuner Network}
For many fabrication problems, tuners cannot act in isolation. For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.  Tuning the free variables as if they were independent usually yields unsatisfactory results. Therefore, we allow the tuners to share information according to a user-specified graph structure.  This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms. For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right).  The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}. The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}. A simplified view of the combined graph is shown in Figure~\ref{fig:combine}. Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.

@@

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.

@@

\subsection{Textured Model}
Here we design an algorithm to print textured models using a two-tone printer. We expand the set of printable colors by stacking translucent materials using the LayeredMaterial node. We then applied dithering with our expanded colors. 
The first two rows in \autoref{tab:result} shows the results of this method.
\subsection{Subsurface Scattering}
We replicated \cite{Hasan:2010} using our framework.

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. 
The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface.
Each tuner is connected to its four neighbors.
During the execution of an individual tuner, the optimization algorithm makes a randomized decision about
 whether or not to swap its micro-lens with one of its neighbors.
The tuners are run in sequence until some convergence criteria is met.
Of note is the fact that this algorithm does not quire a simulation algorithm. 
Despite this it is still implementable within our framework.

In the second algorithm, we use subdivision surfaces to represent a smooth caustic surface. 
This is in contrast to the potentially discontinuous surface in the method above. 
The original algorithm used B-spline surfaces however we have replaced these with a subdivision surface. 
We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}. Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.  A picture of our printed result under desired lighting is shown in \autoref{fig:caustic}.
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

@@

\section{Conclusion}
We have presented Spec2Fab a graph based framework for building fabrication algorithms. By using the Reducer and Tuner Networks we reveal similarities between different fabrication algorithms allowing us to maximize component reuse. This both accelerates and eases implementation. We have also shown how using Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
\section*{Acknowledgements}

>>>>

\section{Introduction}
Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics. These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.

In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment. Given an object one must find a spatially varying material distribution that satisfies some given criteria. The algorithms that solve these problems are often complicated to develop, implement, test and modify. We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new methods.

@@

Fabricating objects with desired mechanical characteristics has been explored less in the literature. Some recent examples include simulating and manufacturing layered composites ~\cite{Bickel:2010} as well as the design and construction of balloons with a prescribed shape while inflated ~\cite{sko:2012}. Finally, material optimization has been employed to create mechanical clones of human faces ~\cite{Bickel:2012}.

@@

Below we will describe the key components of our framework and its associated API. We begin by describing the data structures that tie our framework together, the Reducer Network and the Tuner Network. We will then show how these two components interact to provide a compact graphical description of the material assignment problem. Finally, we will detail the basis set of components that we use to produce a wide-range of fabrication algorithms. 

@@

$\lambda$ can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $ \boldsymbol{\theta}$. We allow our material assignment nodes to assign a void material to regions of the mesh. This allows us to treat surface displacements and material assignments in a unified fashion. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions of the object, however, for material assignment problems this is neither required nor desired.

@@

\subsection{Tuners}
We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.  Specifically a tuner is comprised of an optimization scheme, an error metric and a goal. Each tuner is attached to a specific geometric node in the Reducer Network. It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node. One can think of this as a self-tuning shader network.  This organizational structure allows us to easily optimize subdomains of our object using different tuners. We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing. 
\subsection{Tuning the Reducer Network}
\autoref{fig:tuner0} shows a typical workflow for the tuner.
\begin{figure}
\includegraphics[width=0.4\textwidth]{figure/tuner0.png}
\caption{Typical workflow for a Tuner.}
\label{fig:tuner0}
\end{figure}
A Tuner initializes its optimization procedure by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables. The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables. 
With the search space specified, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine. 
The call-back function typically performs the following three steps:
using Reducer Node to convert a variable assignment back to material assignment
function $\lambda$, running a simulation with the new material assignment
and computing errors given the simulated result.
We note that our material function $\lambda$ can 
be efficiently evaluated by traversing the Reducer Network.
%I need to think about this
%We note that gradient computation of our material function $\lambda$ can also 
%be performed by efficiently traversing the Reducer Network.
\subsection{Tuner Network}
For many fabrication problems, tuners cannot act in isolation. For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.  Tuning the free variables as if they were independent usually yields unsatisfactory results. Therefore, we allow the tuners to share information according to a user-specified graph structure.  This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms. For example, consider the Floyd–Steinberg dithering algorithm in which the error at a given pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right).  The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}. The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}. A simplified view of the combined graph is shown in Figure~\ref{fig:combine}. Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.

@@

%\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.

@@

\subsection{Textured Model}
Here we design an algorithm to print textured models using a two material printer. We expand the set of printable colors by stacking translucent materials using the LayeredMaterial node. We then applied dithering using this expanded gamut. 
The first two rows in \autoref{tab:result} shows the results of this method.
\subsection{Subsurface Scattering}
We replicated \cite{Hasan:2010} using our framework.

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. 
The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface.
Each tuner is connected to its four neighbors.
During the execution of an individual tuner, the optimization algorithm makes a randomized decision about
 whether or not to swap its micro-lens with one of its neighbors.
The tuners are run in sequence until some convergence criteria is met.
Of note is the fact that this method does not require a simulation algorithm. 
Despite this, it is still implementable within our framework.

In the second algorithm, we use subdivision surfaces to represent a smooth caustic surface. 
This is in contrast to the potentially discontinuous surface in the method above. 
The original algorithm used a B-spline surface representation, however we have replaced this with a subdivision surface. 
We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}. Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.  A picture of our printed result under desired lighting is shown in \autoref{fig:caustic}.
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

@@

\section{Conclusion}
We have presented Spec2Fab a graph based framework for building fabrication algorithms. By using the Reducer and Tuner Networks we reveal similarities between different fabrication algorithms allowing us to maximize component reuse. This both accelerates and eases implementation. We have also shown that Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
\section*{Acknowledgements}
